### 2018-03-29 latex/sc18/experiments.tex
experiments section

>>>>

In Figure \ref{fig:ksweepneuro} we compare k-sweeps for $R = 10,20,...,50$ for all 3 algorithms. Starting at $R=10$ we see the largest speed up of $2\times$ for dimensions trees over Liavas. This is due to a combination of the dimension tree performing less flops in the MTTKRPs and KRPs. However, as the rank increases this speed up diminishes to $1.6\times$. The loss of speed up is a result of the fact that, as we observed in \ref{fig:ksweep4DHSI}, the multi-TTV operations do not scale as well as the partial-MTTKRPs for increasing $R$.
